Mahotas: Open source software for scriptable computer vision

### 2012-08-22 paper.tex
TXT More explicit comparison with alternatives

Mahotas is a computer vision library for the Python. It operates on numpy
arrays~\citep{numpystructure}. Therefore, it uses all the infrastructure built
by that project for storing information. In particular, unlike libraries
written in the C~Language or in Java, Mahotas does not need to define a data
structure, but uses the numpy array. Many basic manipulation functionality that
would otherwise be part of a computer vision library are handled by numpy, for
example computing averages and other simple statistics, handling multi-channel
images, converting between types (integer and floating point images are
supported by mahotas, whenever it is meaningful). For the user, this has the
additional advantage that they do not need to learn yet another set of
functions.

@@

Python is an ideal language for fast development of both applications and
scientific software. With a fast library of computer vision and image
processing functions (implemented in \cpp{}, as the standard Python interpreter
is too slow for a direct Python implementation).

>>>>

Mahotas is a computer vision library for the Python. It operates on numpy
arrays~\citep{numpystructure}. Therefore, it uses all the infrastructure built
by that project for storing information. In particular, unlike libraries
written in the C~Language or in Java~\citep{Marcel:2010:TMP:1873951.1874254},
Mahotas does not need to define a data structure, but uses the numpy array
structure. Many basic manipulation functionality that would otherwise be part
of a computer vision library are handled by numpy, for example computing
averages and other simple statistics, handling multi-channel images, converting
between types (integer and floating point images are supported by mahotas,
whenever it is meaningful). For the user, this has the additional advantage
that they do not need to learn yet another set of functions.

@@

Python is an ideal language for fast development of both applications and
scientific software. For this platform, Mahotas is a fast library of computer
vision and image processing functions. It is implemented in \cpp{}, as the
standard Python interpreter is too slow for a direct Python implementation.
However, all of the Python interface code is hand-written, as opposed to using
automatic interface generators like Swig~\cite{Beazley2003599}. This is more
work, but the end result is of much higher quality, especially when it comes to
giving useful error messages (e.g., when a type mismatch occurs, an automatic
system will often be forced to resort to a generic message as it does not have
any knowledge of what the arguments mean besides their automatically inferred
types).
